---
title: "101C Final"
author: "Park"
date: "11/24/2019"
output: pdf_document
---
######################################
#Combine test and train dataset
######################################
```{r}
library(dplyr)
train.full = read.csv("train.csv")
test.full = read.csv("test.csv")
test.full = test.full %>% mutate(HTWins = NA)

######################################
#Row bind train and test dataset
#Drop ID and game ID which we don't need
mix <- rbind(train.full, test.full)
mix <- mix %>% subset(select = -c(id, gameID)) %>% mutate(date = as.Date(as.character(date), "%Y%m%d"))

######################################
#Check the timeline of train and test data
mix %>% filter(!is.na(HTWins)) %>%
  select(date) %>% tail(10)
mix %>% filter(is.na(HTWins)) %>%
  select(date) %>% head(10)
```

######################################
#Delete all the deplicated variable
#Going to delete VT variables not the HT ones
######################################
```{r}
mix <- mix %>% subset(select = -c(VT.TS.fgm, VT.TS.fga, VT.TS.tpm, VT.TS.tpa, VT.TS.fta, VT.TS.oreb, VT.TS.dreb, VT.TS.ast,
                                  VT.TS.stl,VT.TS.blk,VT.TS.to,VT.TS.pf,VT.TS.pts, VT.TA.fga, VT.TA.tpm,VT.TA.tpa,VT.TA.fta, 
                                  VT.TA.oreb, VT.TA.dreb, VT.TA.ast, VT.TA.stl,VT.TA.to, VT.TA.pf, VT.TA.pts,VT.OTS.fgm, 
                                  VT.OTS.fga, VT.OTS.tpm, VT.OTS.tpa, VT.OTS.fta, VT.OTS.oreb, VT.OTS.dreb, VT.OTS.stl, 
                                  VT.OTS.blk, VT.OTS.pf, VT.OTS.pts,VT.OTA.fgm, VT.OTA.fga, VT.OTA.tpa, VT.OTA.fta,
                                  VT.OTA.fta, VT.OTA.blk, VT.OTA.to, VT.OTA.pts, VT.S1.plmin , VT.S3.plmin, VT.S4.plmin, VT.S5.plmin,
                                  VT.OS1.plmin, VT.OS2.plmin, VT.OS3.plmin, VT.OTS.fgm, VT.OTS.fga, VT.OTS.tpm, VT.OTS.tpa,
                                  VT.OTS.fta, VT.OTS.oreb, VT.OTS.dreb, VT.OTS.stl, VT.OTS.blk, VT.OTS.pf, VT.OTS.pts, VT.OTA.fgm,
                                  VT.OTA.fga, VT.OTA.tpa, VT.OTA.fta, VT.OTA.ast, VT.OTA.blk, VT.OTA.to, VT.OTA.pts, VT.TS.fgm,
                                  VT.TS.fga, VT.TS.tpm, VT.TS.tpa, VT.TS.fta, VT.TS.oreb, VT.TS.dreb, VT.TS.ast, VT.TS.stl,
                                  VT.TS.blk, VT.TS.to, VT.TS.pf, VT.TS.pts, VT.TA.fga, VT.TA.tpm, VT.TA.tpa, VT.TA.fta, VT.TA.oreb,
                                  VT.TA.dreb, VT.TA.ast, VT.TA.stl, VT.TA.to, VT.TA.pf, VT.TA.pts, VT.OS1.plmin, VT.OS2.plmin,
                                  VT.OS3.plmin, VT.S1.plmin, VT.S3.plmin, VT.S4.plmin, VT.S5.plmin))
```

######################################
#Make new variables - Zscores
######################################

```{r}
######################################
#Normalize the ability of each player and sum up the zcores of whole players 

#HT.S.plmin by team
mix %>% filter(!is.na(HTWins)) %>% select(HTWins, contains("plm")) %>%
  group_by(HTWins) %>% summarise(mean = mean(HT.S1.plmin))

#function for applying function
express.func <- function(pattern, func){
  return(
    apply(mix[,grepl(pattern, colnames(mix)),drop=F], 1, func)
  )
}

######################################
#Sum of S.plmin
mix <- mix %>% 
  mutate(VT.S.plmin.sum = express.func("^VT.S[0-9].plmin*",sum),
         HT.S.plmin.sum = express.func("^HT.S[0-9].plmin*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.S.sum = mean(VT.S.plmin.sum),
                                 mean.HT.S.sum = mean(HT.S.plmin.sum))

#HT.S.plmin by each team
HT.S.plmin <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.S.plmin.sum = mean(HT.S.plmin.sum),
                             sd.HT.S.plmin.sum = sd(HT.S.plmin.sum))

#VT.S.plmin by each team
VT.S.plmin <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.S.plmin.sum = mean(VT.S.plmin.sum),
                             sd.VT.S.plmin.sum = sd(VT.S.plmin.sum))

#Zscore for HT.S.plmin
mix <- mix %>% left_join(HT.S.plmin, by="HT") %>% 
  mutate(HT.Team.plmin.zscore = (HT.S.plmin.sum-mean.HT.S.plmin.sum)/sd.HT.S.plmin.sum) %>%
  select(subset = -c(mean.HT.S.plmin.sum, sd.HT.S.plmin.sum))

#Zscore for VT.S.plmin
mix <- mix %>% left_join(VT.S.plmin, by="VT") %>% 
  mutate(VT.Team.plmin.zscore = (VT.S.plmin.sum-mean.VT.S.plmin.sum)/sd.VT.S.plmin.sum) %>%
  select(subset = -c(mean.VT.S.plmin.sum, sd.VT.S.plmin.sum))

rm(HT.S.plmin,VT.S.plmin)

######################################
#Sum of S.pts
mix <- mix %>% 
  mutate(VT.S.pts.sum = express.func("^VT.S[0-9].pts*",sum),
         HT.S.pts.sum = express.func("^HT.S[0-9].pts*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.S.sum = mean(VT.S.pts.sum),
                                 mean.HT.S.sum = mean(HT.S.pts.sum))

#HT.S.pts by each team
HT.S.pts <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.S.pts.sum = mean(HT.S.pts.sum),
                             sd.HT.S.pts.sum = sd(HT.S.pts.sum))

#VT.S.pts by each team
VT.S.pts <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.S.pts.sum = mean(VT.S.pts.sum),
                             sd.VT.S.pts.sum = sd(VT.S.pts.sum))

#Zscore for HT.S.pts
mix <- mix %>% left_join(HT.S.pts, by="HT") %>% 
  mutate(HT.Team.pts.zscore = (HT.S.pts.sum-mean.HT.S.pts.sum)/sd.HT.S.pts.sum) %>%
  select(subset = -c(mean.HT.S.pts.sum, sd.HT.S.pts.sum))

#Zscore for VT.S.pts
mix <- mix %>% left_join(VT.S.pts, by="VT") %>% 
  mutate(VT.Team.pts.zscore = (VT.S.pts.sum-mean.VT.S.pts.sum)/sd.VT.S.pts.sum) %>%
  select(subset = -c(mean.VT.S.pts.sum, sd.VT.S.pts.sum))

rm(HT.S.pts,VT.S.pts)

######################################
#Sum of S.min
mix <- mix %>% 
  mutate(VT.S.min.sum = express.func("^VT.S[0-9].min*",sum),
         HT.S.min.sum = express.func("^HT.S[0-9].min*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.S.sum = mean(VT.S.min.sum),
                                 mean.HT.S.sum = mean(HT.S.min.sum))

#HT.S.min by each team
HT.S.min <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.S.min.sum = mean(HT.S.min.sum),
                             sd.HT.S.min.sum = sd(HT.S.min.sum))

#VT.S.pts by each team
VT.S.min <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.S.min.sum = mean(VT.S.min.sum),
                             sd.VT.S.min.sum = sd(VT.S.min.sum))

#Zscore for HT.S.min
mix <- mix %>% left_join(HT.S.min, by="HT") %>% 
  mutate(HT.Team.min.zscore = (HT.S.min.sum-mean.HT.S.min.sum)/sd.HT.S.min.sum) %>%
  select(subset = -c(mean.HT.S.min.sum, sd.HT.S.min.sum))

#Zscore for VT.S.min
mix <- mix %>% left_join(VT.S.min, by="VT") %>% 
  mutate(VT.Team.min.zscore = (VT.S.min.sum-mean.VT.S.min.sum)/sd.VT.S.min.sum) %>%
  select(subset = -c(mean.VT.S.min.sum, sd.VT.S.min.sum))

rm(HT.S.min,VT.S.min)

######################################
#Sum of S.stl
mix <- mix %>% 
  mutate(VT.S.stl.sum = express.func("^VT.S[0-9].stl*",sum),
         HT.S.stl.sum = express.func("^HT.S[0-9].stl*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.S.sum = mean(VT.S.stl.sum),
                                 mean.HT.S.sum = mean(HT.S.stl.sum))

#HT.S.stl by each team
HT.S.stl <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.S.stl.sum = mean(HT.S.stl.sum),
                             sd.HT.S.stl.sum = sd(HT.S.stl.sum))

#VT.S.stl by each team
VT.S.stl <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.S.stl.sum = mean(VT.S.stl.sum),
                             sd.VT.S.stl.sum = sd(VT.S.stl.sum))

#Zscore for HT.S.stl
mix <- mix %>% left_join(HT.S.stl, by="HT") %>% 
  mutate(HT.Team.stl.zscore = (HT.S.stl.sum-mean.HT.S.stl.sum)/sd.HT.S.stl.sum) %>%
  select(subset = -c(mean.HT.S.stl.sum, sd.HT.S.stl.sum))

#Zscore for VT.S.stl
mix <- mix %>% left_join(VT.S.stl, by="VT") %>% 
  mutate(VT.Team.stl.zscore = (VT.S.stl.sum-mean.VT.S.stl.sum)/sd.VT.S.stl.sum) %>%
  select(subset = -c(mean.VT.S.stl.sum, sd.VT.S.stl.sum))

rm(HT.S.stl,VT.S.stl)

######################################
#Sum of S.ast
mix <- mix %>% 
  mutate(VT.S.ast.sum = express.func("^VT.S[0-9].ast*",sum),
         HT.S.ast.sum = express.func("^HT.S[0-9].ast*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.S.sum = mean(VT.S.ast.sum),
                                 mean.HT.S.sum = mean(HT.S.ast.sum))

#HT.S.ast by each team
HT.S.ast <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.S.ast.sum = mean(HT.S.ast.sum),
                             sd.HT.S.ast.sum = sd(HT.S.ast.sum))

#VT.S.ast by each team
VT.S.ast <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.S.ast.sum = mean(VT.S.ast.sum),
                             sd.VT.S.ast.sum = sd(VT.S.ast.sum))

#Zscore for HT.S.ast
mix <- mix %>% left_join(HT.S.ast, by="HT") %>% 
  mutate(HT.Team.ast.zscore = (HT.S.ast.sum-mean.HT.S.ast.sum)/sd.HT.S.ast.sum) %>%
  select(subset = -c(mean.HT.S.ast.sum, sd.HT.S.ast.sum))

#Zscore for VT.S.ast
mix <- mix %>% left_join(VT.S.ast, by="VT") %>% 
  mutate(VT.Team.ast.zscore = (VT.S.ast.sum-mean.VT.S.ast.sum)/sd.VT.S.ast.sum) %>%
  select(subset = -c(mean.VT.S.ast.sum, sd.VT.S.ast.sum))

rm(HT.S.ast,VT.S.ast)

######################################
#Sum of OS.dreb
mix <- mix %>% 
  mutate(VT.OS.dreb.sum = express.func("^VT.OS[0-9].dreb*",sum),
         HT.OS.dreb.sum = express.func("^HT.OS[0-9].dreb*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.OS.sum = mean(VT.OS.dreb.sum),
                                 mean.HT.OS.sum = mean(HT.OS.dreb.sum))

#HT.S.dreb by each team
HT.OS.dreb <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.OS.dreb.sum = mean(HT.OS.dreb.sum),
                             sd.HT.OS.dreb.sum = sd(HT.OS.dreb.sum))

#VT.S.dreb by each team
VT.OS.dreb <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.OS.dreb.sum = mean(VT.OS.dreb.sum),
                             sd.VT.OS.dreb.sum = sd(VT.OS.dreb.sum))

#Zscore for HT.S.dreb
mix <- mix %>% left_join(HT.OS.dreb, by="HT") %>% 
  mutate(HT.Team.OTS.dreb.zscore = (HT.OS.dreb.sum-mean.HT.OS.dreb.sum)/sd.HT.OS.dreb.sum) %>%
  select(subset = -c(mean.HT.OS.dreb.sum, sd.HT.OS.dreb.sum))

#Zscore for VT.S.dreb
mix <- mix %>% left_join(VT.OS.dreb, by="VT") %>% 
  mutate(VT.Team.OTS.dreb.zscore = (VT.OS.dreb.sum-mean.VT.OS.dreb.sum)/sd.VT.OS.dreb.sum) %>%
  select(subset = -c(mean.VT.OS.dreb.sum, sd.VT.OS.dreb.sum))

rm(HT.OS.dreb,VT.OS.dreb)

######################################
#Sum of OS.to
mix <- mix %>% 
  mutate(VT.OS.to.sum = express.func("^VT.OS[0-9].to*",sum),
         HT.OS.to.sum = express.func("^HT.OS[0-9].to*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.OS.sum = mean(VT.OS.to.sum),
                                 mean.HT.OS.sum = mean(HT.OS.to.sum))

#HT.S.to by each team
HT.OS.to <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.OS.to.sum = mean(HT.OS.to.sum),
                             sd.HT.OS.to.sum = sd(HT.OS.to.sum))

#VT.S.to by each team
VT.OS.to <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.OS.to.sum = mean(VT.OS.to.sum),
                             sd.VT.OS.to.sum = sd(VT.OS.to.sum))

#Zscore for HT.S.to
mix <- mix %>% left_join(HT.OS.to, by="HT") %>% 
  mutate(HT.Team.OTS.to.zscore = (HT.OS.to.sum-mean.HT.OS.to.sum)/sd.HT.OS.to.sum) %>%
  select(subset = -c(mean.HT.OS.to.sum, sd.HT.OS.to.sum))

#Zscore for VT.S.to
mix <- mix %>% left_join(VT.OS.to, by="VT") %>% 
  mutate(VT.Team.OTS.to.zscore = (VT.OS.to.sum-mean.VT.OS.to.sum)/sd.VT.OS.to.sum) %>%
  select(subset = -c(mean.VT.OS.to.sum, sd.VT.OS.to.sum))

rm(HT.OS.to,VT.OS.to)

######################################
#Sum of OS.fgm
mix <- mix %>% 
  mutate(VT.OS.fgm.sum = express.func("^VT.OS[0-9].fgm*",sum),
         HT.OS.fgm.sum = express.func("^HT.OS[0-9].fgm*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.OS.sum = mean(VT.OS.fgm.sum),
                                 mean.HT.OS.sum = mean(HT.OS.fgm.sum))

#HT.S.fgm by each team
HT.OS.fgm <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.OS.fgm.sum = mean(HT.OS.fgm.sum),
                             sd.HT.OS.fgm.sum = sd(HT.OS.fgm.sum))

#VT.S.fgm by each team
VT.OS.fgm <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.OS.fgm.sum = mean(VT.OS.fgm.sum),
                             sd.VT.OS.fgm.sum = sd(VT.OS.fgm.sum))

#Zscore for HT.S.fgm
mix <- mix %>% left_join(HT.OS.fgm, by="HT") %>% 
  mutate(HT.Team.OTS.fgm.zscore = (HT.OS.fgm.sum-mean.HT.OS.fgm.sum)/sd.HT.OS.fgm.sum) %>%
  select(subset = -c(mean.HT.OS.fgm.sum, sd.HT.OS.fgm.sum))

#Zscore for VT.S.fgm
mix <- mix %>% left_join(VT.OS.fgm, by="VT") %>% 
  mutate(VT.Team.OTS.fgm.zscore = (VT.OS.fgm.sum-mean.VT.OS.fgm.sum)/sd.VT.OS.fgm.sum) %>%
  select(subset = -c(mean.VT.OS.fgm.sum, sd.VT.OS.fgm.sum))

rm(HT.OS.fgm,VT.OS.fgm)

######################################
#Sum of OS.oreb
mix <- mix %>% 
  mutate(VT.OS.oreb.sum = express.func("^VT.OS[0-9].oreb*",sum),
         HT.OS.oreb.sum = express.func("^HT.OS[0-9].oreb*",sum))

mix %>% filter(!is.na(HTWins)) %>% 
  group_by(HTWins) %>% summarise(mean.VT.OS.sum = mean(VT.OS.oreb.sum),
                                 mean.HT.OS.sum = mean(HT.OS.oreb.sum))

#HT.S.oreb by each team
HT.OS.oreb <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(HT) %>% summarise(mean.HT.OS.oreb.sum = mean(HT.OS.oreb.sum),
                             sd.HT.OS.oreb.sum = sd(HT.OS.oreb.sum))

#VT.S.oreb by each team
VT.OS.oreb <- mix %>% filter(!is.na(HTWins)) %>%
  group_by(VT) %>% summarise(mean.VT.OS.oreb.sum = mean(VT.OS.oreb.sum),
                             sd.VT.OS.oreb.sum = sd(VT.OS.oreb.sum))

#Zscore for HT.S.oreb
mix <- mix %>% left_join(HT.OS.oreb, by="HT") %>% 
  mutate(HT.Team.OTS.oreb.zscore = (HT.OS.oreb.sum-mean.HT.OS.oreb.sum)/sd.HT.OS.oreb.sum) %>%
  select(subset = -c(mean.HT.OS.oreb.sum, sd.HT.OS.oreb.sum))

#Zscore for VT.S.oreb
mix <- mix %>% left_join(VT.OS.oreb, by="VT") %>% 
  mutate(VT.Team.OTS.oreb.zscore = (VT.OS.oreb.sum-mean.VT.OS.oreb.sum)/sd.VT.OS.oreb.sum) %>%
  select(subset = -c(mean.VT.OS.oreb.sum, sd.VT.OS.oreb.sum))

rm(HT.OS.oreb,VT.OS.oreb)
```

######################################
#One Hot Encoding
#This will convert categorical variables into the combination matrix of 0,1.
#Adds more than 50 columns but I think it's worth addining them.
######################################

------------

```{r}
library(tidyverse)
library(lubridate)
library(caret)
#Separate date into year, month, and day
#mix = mix %>% 
#  mutate(date = ymd(date)) %>% 
#  mutate_at(vars(date), funs(year, month, day))

#Change date variable to weekdays
mix = mix %>% mutate(wd = as.factor(weekdays(as.Date(date)))) %>% select(subset = -c(date))

mix.new <- mix %>% subset(select = c(HTWins, HTleague, VTleague, HT, VT, wd))

#one hot encoding
dummies <- dummyVars(~VT + HT + VTleague + HTleague + wd, data=mix.new)
dummies.pred <- predict(dummies, mix.new)
mix.onehot <- cbind(mix.new, dummies.pred)
mix.onehot <- mix.onehot %>% select(subset=-c(VT,HT,VTleague,HTleague,wd))

mix.onehot %>% select_if(is.factor) %>% colnames

mix %>% select_if(is.factor) %>% colnames
mix <- mix %>% select(subset=-c(VT,HT,VTleague,HTleague,wd))
mix.onehot <- mix.onehot %>% select(subset=-c(HTWins))

#Merge one hot encoding into the mix dataset
total.mix = cbind(mix, mix.onehot)

rm(mix.new, mix.onehot, dV, dv.pred, dummies, dummies.pred)
```

######################################
#Plots to find or check the pattern of variables
######################################

```{r}
##See the overall pattern of data
library(ggplot2)
#Home team field goal made / attempted
#Kind of sig
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.TS.fgm/HT.TS.fga)) + geom_boxplot()

#Home team, opposing team field goal made / attempted
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.OTS.fgm/HT.OTS.fga)) + geom_boxplot()

#Home team three point goal made / attempted
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.TS.tpm/HT.TS.tpa)) + geom_boxplot()

#Home team, opposing team three point goal made/attempted
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.OTS.tpm/HT.OTS.tpa)) + geom_boxplot()

#Home team scored offensive rebound / defensive rebound
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.TS.oreb/HT.TS.dreb)) + geom_boxplot()

#Home team free throws scored / allowed
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.TS.fta/HT.TA.fta)) + geom_boxplot()

#Home team rest / total rest
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HTcumRest/(VTcumRest + HTcumRest))) + geom_boxplot()

#Home team scored personal foul / total foul
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.TS.pf/(HT.TA.pf +HT.TS.pf))) + geom_boxplot()

#Home team scored block / total block
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.TS.blk/(HT.TS.blk +HT.TA.blk))) + geom_boxplot()

#Home team scored field goal made / total fgm
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.TS.fgm/(HT.TS.fgm +HT.OTS.fgm))) + geom_boxplot()

#Home
mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.Team.plmin.zscore)) + geom_boxplot()

mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = VT.Team.plmin.zscore)) + geom_boxplot()

mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.Team.pts.zscore)) + geom_boxplot()

mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = VT.Team.pts.zscore)) + geom_boxplot()

mix %>% filter(!is.na(HTWins)) %>% ggplot(aes(x = HTWins, y = HT.Team.min.zscore)) + geom_boxplot()
```

######################################
#GLM to check the significance of the coefficients
######################################
```{r}
total.mix.train = total.mix %>% filter(!is.na(HTWins))
mix.glm = glm(HTWins ~ ., total.mix.train, family = "binomial")
summary(mix.glm)
```

######################################
#Tree base model for prediction
######################################

```{r}
library(randomForest)
train = total.mix %>% filter(!is.na(HTWins))
test = total.mix %>% filter(is.na(HTWins))
model1 <- randomForest(HTWins ~ ., data = train, ntree = 500, mtry = 6, importance = TRUE)
model1
predTrain <- predict(model1, train, type = "class")
table(predTrain, train$HTWins)

######################################
#See the importance of each variable
varImpPlot(model1)

######################################
#Output predict csv file for Kaggle upload
predValid <- predict(model1, test, type = "class")
samplecsv = data.frame(id = test.full$id, HTWins = predValid)
write.csv(samplecsv, file = "submit.csv", row.names = F)
```

######################################
#Ensemble Method
######################################

```{r}
library(mlbench)
library(caretEnsemble)
library("SuperLearner")
library(ranger)
 
#Change response variable type
#Load variable
y <- as.numeric(train$HTWins)-1
ytest <- as.numeric(test$HTWins)-1
x <- data.frame(train[,-1])
xtest <- data.frame(test[,-1])

listWrappers()

set.seed(150)
single.model <- SuperLearner(y,
                             x,
                             family=binomial(),
                             SL.library=list("SL.ranger"))

single.model

set.seed(150)

# Fit the ensemble model
model <- SuperLearner(y,
                      x,
                      family=binomial(),
                      SL.library=list("SL.ranger",
                                     "SL.ksvm",
                                     "SL.ipredbagg",
                                     "SL.bayesglm"))

# Return the model
model

# Set the seed
set.seed(150)

# Get V-fold cross-validated risk estimate
cv.model <- CV.SuperLearner(y,
                            x,
                            V=5,
                            SL.library=list("SL.ranger",
                                            "SL.ksvm",
                                            "SL.ipredbagg",
                                            "SL.bayesglm"))

# Print out the summary statistics
summary(cv.model)

plot(cv.model)

predictions <- predict.SuperLearner(model, newdata=xtest)
head(predictions$pred)
head(predictions$library.predict)
conv.preds <- as.factor(ifelse(predictions$pred>=0.5,"Yes", "No"))

#Output predict csv file for Kaggle upload
samplecsv = data.frame(id = test.full$id, HTWins = conv.preds)
write.csv(samplecsv, file = "sample.csv", row.names = F)
```
